# Week 3 Project

## Van Anh Le

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

###Deconstructing graphics

- This is a density plot.

- The variables involved are bmi, sex, pregnant.

- bmi is a frame, pregnant (yes or no) serves as a facet, sex is mapped on to the color aesthetics. 

- This is a density plot. The value on the y-axis is the density of values of bmi in the data. 

```{r}
library(mosaicData)
ggplot(data = CPS85, aes(x = exper, y = wage, color = married)) + geom_point() + facet_wrap( ~sector)
```
```{r}
ggplot(data = NCHS, aes(x = bmi)) + geom_density(aes(color = sex)) + facet_wrap(~pregnant)
```

###Wrangling

####Diamonds

```{r}
diamonds %>%
  group_by(color)%>%
  summarize(mean=mean(carat))%>%
  arrange(desc(mean))%>%
    head(1)
```

On average, J colored diamonds weigh the most. 

```{r}
diamonds%>%
  group_by(clarity)%>%
  summarize(mean=mean(table))%>%
  arrange(desc(mean))%>%
    head(1)
```

On average, diamonds with l1 clarity has the largest "table" per carat.

####Voting

```{r}
Minneapolis2013%>%
  tally()
```

There are 80101 cases. 

The top 5 candidates in Second vote are:
```{r}
Minneapolis2013%>%
  group_by(Second)%>%
  summarize(topSecond = n()) %>%
  arrange(desc(topSecond))
```

```{r}
Minneapolis2013 %>%
  summarise(first_undervote = sum(First == "undervote"),
            second_undervote=sum(Second == "undervote"),
            third_undervote=sum(Third == "undervote"))
```
```{r}
Minneapolis2013%>%
  filter(First =="BETSY HODGES")%>%
  group_by(Second)%>%
  summarize(top3 = n())%>%
  arrange(desc(top3))%>%
  head(3)

``` 

```{r}
Minneapolis2013%>%
  group_by(Precinct)%>%
  summarize(fraction=mean(First == "undervote"))%>%
  arrange(desc(fraction))
```